Documentation FFI Sonar Simulator

### 2013-05-23 FFI-Simulator/ffi-simulator.tex
la2pdf commit - 2013:05:23	19:54:13	(Thu23.May)

If the answer to this is no, then we propose using a OpenGL to simulate the scene, and model the array as lightsources. Geometrical effects can be added in the post-processing using CUDA / OpenCL, but extending the simulator to support other sonar specific effects will likely be hard. This approach with also be very portable, and should not require too much effort.

@@

We aim to start development in July. The goal is to have an OpenGL prototype ready within a couple weeks, and from there decide which approach to go for. We propose monthly progress reports and meetings to discuss further development.

@@

>>>>

If the answer to this is no, then we propose using a OpenGL to simulate the scene, and model the array as light sources. Geometrical effects can be added in the post-processing using CUDA / OpenCL, but extending the simulator to support other sonar specific effects will likely be hard. On the upside this approach will be very portable, and should not require too much effort.

@@

We aim to start development in July. The goal is to have an OpenGL prototype ready within a couple weeks, and from there decide which approach to go for. We propose monthly progress reports and meetings to discuss further development. See our specification on the next page.

@@

\begin{tabular}[c]{l p{0.6\linewidth}}
Development time       & 4-6 weeks per person  \\
Our price              & 98\;000 NOK \\
We deliver        & 
\end{tabular}
\begin{itemize0}
\item A fully functional simulator with the features requested.
\item Support up to 6 months after delivery.
\item Through documentation.
\item All rights to use, alter and redistribute the code in whatever way the customer see fit.
\end{itemize0}
\begin{tabular}[c]{l p{0.6\linewidth}}
We reserve the right to &
\end{tabular}
\begin{itemize0}
\item Use the code and ideas obtained during the development of this simulator for research purposes, but only with the consent of FFI.
\end{itemize0}
